Paper Plan\\ FF-Replan: \& RFF\@: Exploiting classical AI planning for uncertain and probabilistic domains

### 2014-03-11 paper-plan/paper-plan.tex
move hindsight of 2008
Adding Improving Determinization of hindsight planning

@@

Hindsight optimization is an online technique that evaluates one-step-reachable
states by sampling future outcomes to generate multiple non-stationary planning
problems which are deterministic and can be used using search. It re-interprets
FF-Replan's~\ref{FFReplan} strategy randomly generating a set of non-stationary
determinized problems and combining their solutions.

\subsubsection{Progressive heuristic search for probabilistic planning based on interaction estimates (2013)~\ref{martin2013progressive}}

>>>>

Hindsight optimization is an online technique that evaluates one-step-reachable
states by sampling future outcomes to generate multiple non-stationary planning
problems which are deterministic and can be used using search. It re-interprets
FF-Replan's~\cite{FFReplan} strategy randomly generating a set of non-stationary
determinized problems and combining their solutions.

\subsubsection{Improving Determinization in Hindsight for Online Probabilistic Planning (2010)~\cite{yoon2010improving}}

Hindsight optimization has enjoyed some success for online probabilistic
planning. Although it has proven to be effective for many domains, it is
computationally expensive. This paper presents significant improvements.  1) a
method for detecting potential useful actions, 2) exploit determinism in the
domain by reusing relevant plans, 2) improves action evaluation by increasing
the chance that at least one deterministic plan reaches a goal.

@@

\subsubsection{Progressive heuristic search for probabilistic planning based on interaction estimates (2013)~\cite{martin2013progressive}}
